Supplemental Materials, Methods and Results

### 2021-05-07 supp.Rmd
Re-oragnised tables and figures so they flow on from each other. Renamed chuncks

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp, png, cowplot, magick, jpeg, clubSandwich)
source("./R/func.R")
```

@@

### Changes in visual signals across body regions show similar patterns
We took measurements of spectral reflectance for different body regions of each chamaleon. In our primary analysis, we averaged across different body regions because we were interested only in whether visual signals were different in Kenya and Hawaii overall. This was justified given that, across the different body regions, effects were largely in a similar direction, and often of similar magnitude (Figures \@ref(fig:FigS1), \@ref(fig:FigS2), \@ref(fig:FigS3)) and Tables \@ref(tab:tableS1), \@ref(tab:tableS2)).

```{r tableS1, tab.cap = "Pairwise comparisons of achormatic contrast between Kenyan and Hawaiian chameleon displays to a snake and bird visual system. Four different body regions ('gular', 'midflank', 'tailbase', topflank') are provided along with pairwise Wald test for contrast significance. Wald test uses a robust variance correction on the standard errors."}

```{r tableS2, tab.cap = "Pairwise comparisons of achormatic contrast between Kenyan and Hawaiian chameleon displays to a snake and bird visual system. Four different body regions ('gular', 'midflank', 'tailbase', topflank') are provided along with pairwise Wald test for contrast significance. Wald test uses a robust variance correction on the standard errors."}

```{r tableS3, tab.cap = "Wald Tests comparing significance of model parameters. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}
fullTable <- rbind(wald_table_ConspicDisplayAC, 
                   wald_table_ConspicDisplayCC, 
                   wald_table_ConspicCourtshipAC,
                   wald_table_ConspicCourtshipCC)

```{r table4, tab.cap = "Wald Tests comparing significance of model parameters for predators. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}

@@

@@

>>>>

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp, png, cowplot, magick, jpeg, clubSandwich, flextable)
source("./R/func.R")
```

@@

### Changes in visual signals across body regions show similar patterns
We took measurements of spectral reflectance for different body regions of each chamaleon. In our primary analysis, we averaged across different body regions because we were interested only in whether visual signals were different in Kenya and Hawaii overall. This was justified given that, across the different body regions, effects were largely in a similar direction, and often of similar magnitude (Figures \@ref(fig:FigS1), \@ref(fig:FigS2), \@ref(fig:FigS3)) and Tables \@ref(tab:tableS1), \@ref(tab:tableS2), \@ref(tab:tableS3), \@ref(tab:tableS4). \@ref(tab:tableS5)).

@@

```{r tableS2, tab.cap = "Wald Tests comparing significance of model parameters. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}
fullTable <- rbind(wald_table_ConspicDisplayAC, 
                   wald_table_ConspicDisplayCC, 
                   wald_table_ConspicCourtshipAC,
                   wald_table_ConspicCourtshipCC)

```{r tableS3, tab.cap = "Linear mixed effects model results using sandwich estimators and Saitterwaite degrees of freedom correction.Social Context"}
robust_sc_table <- rbind(robust_ConspicDisplayAC,
                          robust_ConspicDisplayCC,
                          robust_ConspicCourtshipAC,
                          robust_ConspicCourtshipCC) %>% 
                    mutate(p_Satt = sapply(p_Satt, function(x) p_value(x)),
                           SocialContext = c("Male-Male Display", rep("", 17), 
                                             "Courtship Display", rep("", 17)),
                           JND = c("Achromatic Contrast", rep("", 8), 
                                   "Chromatic Contrast", rep("", 8), 
                                   "Achromatic Contrast", rep("", 8), 
                                   "Chromatic Contrast", rep("", 8)))

robust_sc_table$parameter <- rownames(robust_sc_table)

robust_sc_table <- robust_sc_table %>% select(SocialContext, JND, parameter, beta, SE, tstat, df, p_Satt)

tableS5 <- flextable(robust_sc_table) %>%  table_style4()
tableS5
```

@@

```{r tableS4, tab.cap = "Wald Tests comparing significance of model parameters for predators. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}

```{r tableS5, tab.cap = "Linear mixed effects model results using sandwich estimators and Saitterwaite degrees of freedom correction.Predators"}
robust_sc_pred_table <- rbind(robust_PredatorAC,
                         robust_PredatorCC) %>% 
                    mutate(p_Satt = sapply(p_Satt, function(x) p_value(x)),
                           JND = c("Achromatic Contrast", rep("", 9), 
                                   "Chromatic Contrast", rep("", 9)))

robust_sc_pred_table$parameter <- rownames(robust_sc_pred_table)

robust_sc_pred_table <- robust_sc_pred_table %>% select(JND, parameter, beta, SE, tstat, df, p_Satt)

tableS6 <- flextable(robust_sc_pred_table) %>%  table_style5()
tableS6
```

```{r tableS6, tab.cap = "Pairwise comparisons of achormatic contrast between Kenyan and Hawaiian chameleon displays to a snake and bird visual system. Four different body regions ('gular', 'midflank', 'tailbase', topflank') are provided along with pairwise Wald test for contrast significance. Wald test uses a robust variance correction on the standard errors."}

```{r tableS7, tab.cap = "Pairwise comparisons of achormatic contrast between Kenyan and Hawaiian chameleon displays to a snake and bird visual system. Four different body regions ('gular', 'midflank', 'tailbase', topflank') are provided along with pairwise Wald test for contrast significance. Wald test uses a robust variance correction on the standard errors."}
